Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2019-11-12 writing/ehp_abstract.tex
Work some more on abstract and small wording

\noindent \textbf{Background:} 
        Tropical cyclone epidemiology can be 
	advanced through methods to assess 
	county-level exposure to storm hazards, particularly 
	methods that are comprehensive and 
	consistent across space and time, allowing multi-year, multi-storm studies. 
	Further, an understanding of 
	patterns in and between hazard-specific exposure metrics can help in 
	designing tropical cyclone epidemiological studies.\\ 
\textbf{Objectives:} (1)~Provide an open-source dataset to improve tropical
	cyclone exposure assessment for epidemiological research and
	(2)~investigate patterns and agreement between county-level assessments of tropical cyclone
	exposure based on different storm hazards. \\ 
\textbf{Methods:} We created an open-source dataset with county-level data on
	exposure to four tropical cyclone hazards: maximum sustained winds,
	rainfall, flooding, and tornadoes. The data cover all eastern \ac{US} counties 
	for all land-falling or near-land
	Atlantic basin storms for~1996\,--\,2011 for all
	metrics (up to~1988\,--\,2015 for specific metrics). 	
	We validated 
	measurements against other data sources and investigated patterns
	and agreement among binary exposure classifications based on these
	metrics. We also compared exposure assessment
	based on using distance between a county and the storm's track as a proxy for
	storm exposure.\\ 
\textbf{Results:} Measurements in the open-source dataset created here typically
        agreed with data from other sources, and we present and discuss areas of
	disagreement and other caveats for using the data.
        Long-term geographic patterns in binary 
	classifications based on these data agree with previous results from
	atmospheric science. County-level exposure classification for a storm differs substantially 
	depending on the hazard metric used. \\ 
\textbf{Discussion:} Our results provide a multi-hazard dataset that can be
	leveraged for epidemiologic research on tropical cyclones.  Further,	
	our results suggest that the use of distance as a
	surrogate for tropical cyclone exposure, or use one hazard-based metric
	when the impact is partly or fully caused by a different hazard, would often 
	result in exposure misclassification in epidemiological studies.  
\end{abstract}

>>>>

\noindent \textbf{Background:} 
        Tropical cyclone epidemiology can be 
	advanced through county-level exposure assessment methods that are comprehensive and 
	consistent across space and time, allowing multi-year, multi-storm studies. 
	Further, an understanding of 
	patterns in and between hazard-specific exposure metrics can help in 
	designing tropical cyclone epidemiological studies.\\ 
\textbf{Objectives:} (1)~Provide an open-source dataset for tropical
	cyclone exposure assessment for epidemiological research and
	(2)~investigate patterns and agreement between county-level assessments of tropical cyclone
	exposure based on different storm hazards. \\ 
\textbf{Methods:} We created an open-source dataset with county-level data on
	exposure to four tropical cyclone hazards: maximum sustained winds,
	rainfall, flooding, and tornadoes. The data cover all eastern \ac{US} counties 
	for all land-falling or near-land
	Atlantic basin storms for~1996\,--\,2011 for all
	metrics and up to~1988\,--\,2015 for specific metrics. 	
	We validated 
	measurements against other data sources and investigated patterns
	and agreement among binary exposure classifications based on these
	metrics, as well as between distance from the storm's track as a proxy for
	exposure.\\ 
\textbf{Results:} Measurements in the dataset created here typically
        agreed with data from other sources, and we present and discuss areas of
	disagreement and other caveats for the data.
        Long-term geographic patterns in exposure classification agree with previous results from
	atmospheric science. County-level exposure classification for a storm differs substantially 
	depending on the hazard metric used. \\ 
\textbf{Discussion:} Our results provide a multi-hazard dataset that can be
	leveraged for epidemiologic research on tropical cyclones, as well as 
	insights that can inform the design of tropical cyclone epidemiological 
	studies.
\end{abstract}

### 2019-11-12 writing/ehp_discussion.tex
Work some more on abstract and small wording

Epidemiological studies can help characterize which health risks are elevated
during disasters, to what degree, and to
whom~\parencite{ibrahim2005unfortunate, noji2005disasters}.  As a result, these
studies help improve disaster preparedness and
response~\parencite{noji2005disasters}.  However, tropical cyclones are
multi-hazard events, making it complicated to measure exposure and so to
conduct multi-community, multi-year studies leveraging large administrative
datasets.  Here, we provide open-source county-level data on multiple tropical
cyclone exposure metrics and explore limitations in that data.  
Further, we explore patterns in storm exposure classifications based on
different metrics, and we find that county-level tropical cyclone exposure
assessments vary substantially when using different metrics, based either on
storm hazards or on how close the storm's central track came to the community.
Our results can inform exposure assessment for future county-level studies of
the health risks and impacts associated with tropical cyclones exposures as
well as insights to help in designing studies.

@@

This disagreement highlights the difficulty of large-scale pairing of storm
tracks with storm event listings---without criteria for temporally matching
event start dates to storm dates, many false positives would be
captured, for which the occurrance of a storm in the midst of an ongoing storm
event might be improperly attributed to the storm.  However, distance
and time restrictions, like those we used in matching NOAA Storm Event listings
with tropical storm locations and dates, do create the opportunity for
occasional false negatives, as for Hurricane Ida in Fulton County, GA, where a
storm contributes meaningfully to an ongoing event, but the event is not
captured for the storm in the exposure data.

@@

We found that tropical cyclones tended to bring different hazards to different
counties and also that agreement was typically low between distance-based
tropical cyclone exposure assessment and each of the single hazard-specific
exposures, as well as between pairs of hazard-specific metrics
(Figures~\ref{fig:ivanexposure}\,--\,\ref{fig:jaccard} and S4\,--\,S5).  These
findings align with previous results from atmospheric science and related
fields on the characteristics of tropical cyclones. While tropical cyclone
rainfall and windspeed can be well-correlated when the tropical cyclone is over
water~\parencite{cerveny2000}, this relationship often weakens once the
hurricane has made landfall~\parencite{jiang2008}.  Fast-moving tropical
cyclones bring higher risks of dangerous winds inland~\parencite{kruk2010},
while slow-moving tropical cyclones are likely to bring more
rain~\parencite{rappaport2000} and cause more damage because of sustained
hazardous conditions~\parencite{rezapour2014}. Further, while the likelihood
and extent of flooding during a tropical cyclone is related to the tropical
cyclone's rainfall, it is also driven by factors like top soil saturation and
the structure of the water basin's drainage network~\parencite{chen2015,
rees2001}.

@@

The dataset presented here does have several limitations, in addition to the
caveats previously discussed. First, the dataset is not comprehensive of all
possible tropical cyclone hazards. For example, coastal counties can experience
dangerous storm surge, which is not specifically covered in this dataset
(although some resulting coastal flooding is captured). We are exploring ways to
include this in future versions of the dataset, although to date we have
focused on exposures that could affect any county, whether inland or coastal.
Second, this data is aggregated to the county level. Many health outcome
datasets are aggregated at this level, but some may be aggregated at a finer
spatial resolution (e.g., Census tract or ZIP code) or unaggregated (i.e., point locations
for each outcome). We have published the wind
model we used to create this dataset as its own open-source R package
\parencite{stormwindmodel}, and it can be used to model
storm-associated winds at a finer spatial resolution; however, measurements of
other hazards cannot similarly be re-scaled through tools we provide. Next,
we provide these data and associated software tools through R packages, and so
some experience in the R programming language is required to make full use of
them. However, R is currently a popular programming language for environmental
epidemiology, allowing the data to reach a large audience, and we are exploring
options to create a web application using the Shiny platform to allow more
user-friendly web-based access of the data \parencite{shiny2019}. 
Finally, to assess patterns and agreement for binary exposure classifications, 
we have chosen one set of sensible thresholds for binary classifications based
on continuous metrics (rainfall, maximum sustained winds, and distance from 
the storm's track). Results and conclusions would differ somewhat with other
threshold choices. We have published all our code for this analysis online
[web address], in case other researchers would like to explore other 
threshold choices for these analyses.

@@

To conduct tropical cyclone epidemiological studies that span multiple
communities and storms, it is critical to have consistent and comprehensive
measurements of exposure to storm hazards. Here we have created and shared a
dataset that provides these data for counties in the United States over
multiple years. Despite some limitations in these data, they provide a powerful
tool for expanding tropical cyclone epidemiology studies to more extensively
leverage existing administrative health data, allowing researchers to
investigate how these storms affect county-wide health risk, including for
outcomes also common outside of storm periods.  Further, this dataset provides
hazard measurements that are comparable across communities and storms, which
allows epidemiological researchers to design studies to explore how health
risks are modified by characteristics of both the storms and the communities
that are hit. The data are given in an open-source format, along with
associated software tools, which allows them to be freely used and for others
to explore all associated code and to contribute additions through platforms
like GitHub.

Based on our analysis in this paper, these data are typically in agreement with
measurements from other sources of data available to characterize
storm-associated hazards (e.g., ground-based monitors, streamgages, post-storm
wind radii estimates).  However, researchers who are planning to use the data
should explore the analyses presented in this paper to understand the strengths
and weaknesses of the data.  Our results suggest that county-level storm
exposure is not well-characterized by the closest distance that a storm's
central track came to a county, and that exposure to one storm hazard within a
county (e.g., severe winds) does not imply exposure to other hazards (e.g.,
excessive rainfall, flooding). As a result, it is critical that researchers
consider which storm hazards are likely on the causal pathway for the outcomes
they are studying, and to characterize storm exposure in a way that captures
those specific hazards.

>>>>

Epidemiological studies can help characterize which health risks are elevated
during disasters, to what degree, and to
whom~\parencite{ibrahim2005unfortunate, noji2005disasters}.  As a result, these
studies help improve disaster preparedness and
response~\parencite{noji2005disasters}.  However, tropical cyclones are
multi-hazard events, making it complicated to measure exposure and so to
conduct multi-community, multi-year studies leveraging large administrative
datasets.  Here, we provide open-source county-level data on multiple tropical
cyclone exposure metrics and explore limitations in that data.  
Further, we explore patterns in storm exposure classifications based on
different metrics, and we find that county-level tropical cyclone exposure
assessments vary substantially when using different metrics, based either on
storm hazards or on how close the storm's central track came to the community.
Our results can inform exposure assessment for future county-level studies of
the health risks and impacts associated with tropical cyclones exposure as
well as insights to inform epidemiological study design.

@@

This disagreement highlights the difficulty of large-scale pairing of storm
tracks with storm event listings---without criteria for temporally matching
event start dates to storm dates, many false positives would be
captured, for which the occurrance of a storm in the midst of an ongoing storm
event might be improperly attributed to the storm.  However, distance
and time restrictions, like those we used in matching NOAA Storm Event listings
with tropical cyclone locations and dates, do create the opportunity for
occasional false negatives, as for Hurricane Ida in Fulton County, GA, where a
storm contributes meaningfully to an ongoing event, but the event is not
captured for the storm in the exposure data.

@@

We found that tropical cyclones tended to bring different hazards to different
counties, and so agreement was typically low between distance-based
tropical cyclone exposure assessment and each of the single hazard-specific
exposures, as well as between pairs of hazard-specific metrics
(Figures~\ref{fig:ivanexposure}\,--\,\ref{fig:jaccard} and S4\,--\,S5).  These
findings align with previous results from atmospheric science and related
fields on the characteristics of tropical cyclones. While tropical cyclone
rainfall and windspeed can be well-correlated when the tropical cyclone is over
water~\parencite{cerveny2000}, this relationship often weakens once the
hurricane has made landfall~\parencite{jiang2008}.  Fast-moving tropical
cyclones bring higher risks of dangerous winds inland~\parencite{kruk2010},
while slow-moving tropical cyclones are likely to bring more
rain~\parencite{rappaport2000} and cause more damage because of sustained
hazardous conditions~\parencite{rezapour2014}. Further, while the likelihood
and extent of flooding during a tropical cyclone is related to the tropical
cyclone's rainfall, it is also driven by factors like top soil saturation and
the structure of the water basin's drainage network~\parencite{chen2015,
rees2001}.

@@

The dataset presented here does have several limitations, in addition to the
caveats previously discussed. First, the dataset is not comprehensive of all
possible tropical cyclone hazards. For example, coastal counties can experience
dangerous storm surge, which is not specifically covered in this dataset
(although some resulting coastal flooding is captured). We are exploring ways
to include this in future versions of the dataset, although to date we have
focused on exposures that could affect any county, whether inland or coastal.
Second, this data is aggregated to the county level. Many health outcome
datasets are aggregated at this level, but some may be aggregated at a finer
spatial resolution (e.g., Census tract or ZIP code) or unaggregated (i.e.,
point locations for each outcome). We have published the wind model used to
create this dataset as its own open-source R package
\parencite{stormwindmodel}, and it can be used to model storm-associated winds
at a finer spatial resolution; however, measurements of other hazards cannot
similarly be re-scaled through tools we provide. Next, we provide these data
and associated software tools through R packages, and so some experience in the
R programming language is required to make full use of them. However, R is
currently a popular programming language for environmental epidemiology,
allowing the data to reach a large audience, and we are exploring options to
create a web application using the Shiny platform to allow broader web-based
access of the data \parencite{shiny2019}.  Finally, to assess patterns and
agreement for binary exposure classifications, we have chosen one set of
sensible thresholds for binary classifications based on continuous metrics
(rainfall, maximum sustained winds, and distance from the storm's track).
Results and conclusions would differ somewhat with other threshold choices. We
have published code for this analysis online, allowing
other researchers can explore other threshold choices for these
analyses.

@@

To conduct tropical cyclone epidemiological studies that span multiple
communities and storms, it is critical to have consistent and comprehensive
measurements of exposure to storm hazards. Here we have created and shared a
dataset that provides these data for counties in the United States over
multiple years. Despite some limitations in these data, they provide a powerful
tool for expanding tropical cyclone epidemiology studies to more extensively
leverage existing administrative health data, allowing researchers to
investigate how these storms affect county-wide health risk.  Further, this
dataset provides hazard measurements that are comparable across communities and
storms, which allows epidemiological researchers to design studies to explore
how health risks are modified by characteristics of both the storms and the
communities that are hit. The data are given in an open-source format, along
with associated software tools, which allows them to be freely used and for
others to explore all associated code and to contribute additions through
platforms like GitHub.

Based on our analysis in this paper, these data are typically in agreement with
measurements from other sources of data available to characterize
storm-associated hazards (e.g., ground-based monitors, streamgages, post-storm
wind radii estimates).  However, researchers who are planning to use the data
should explore the analyses presented in this paper to understand the strengths
and weaknesses of the data.  Our results suggest that county-level storm
exposure is not well-characterized by the closest distance that a storm's
central track came to a county, and that exposure to one storm hazard within a
county (e.g., severe winds) does not imply exposure to other hazards (e.g.,
excessive rainfall, flooding). As a result, it is critical that researchers
consider which storm hazards are likely on the causal pathway for the outcomes
they are studying, and to characterize storm exposure in a way that captures
those specific hazards, to avoid exposure misclassification.

### 2019-11-12 writing/ehp_introduction.tex
Work some more on abstract and small wording

Hurricanes and other tropical cyclones can severely impact human health in
\ac{US} communities, and some of these impacts have been characterized through
multi-year studies based on fatality data from post-disaster
surveillance~\parencite{rappaport2000, rappaport2014fatalities,
rappaport2016fatalities, czajkowski2010fatal, czajkowski2011, moore2012}.  For
several types of climate-related disasters---including heat waves, floods, and
wildfires---research based on post-disaster surveillance data has been richly
supplemented by studies analyzing trends in community-wide administrative or
vital data, including time series or case-crossover studies
(e.g.,~\cite{anderson2010heat, son2012impact, haikerwal2015impact,
liu2017wildfire, milojevic2017mental}).  These studies typically compare the
rate of a health outcome in a community during a disaster to rates during
comparable non-disaster periods.  While these studies cannot attribute specific
cases (e.g., a specific person's death) to a disaster, they can help
characterize the community-wide change in health risk during disasters and
capture impacts that might be missed or underestimated in post-disaster
surveillance.  In many cases, these studies analyze multi-year, multi-community
data, allowing them to estimate average associations over many disasters and to
explore how a disaster's characteristics, or the characteristics of the
community it hits, modify associated health risks (e.g.,~\cite{anderson2010heat,
son2012impact, liu2017wildfire}).  Some studies have begun to use this approach
to study the health impacts of tropical cyclones, including several studies of
Hurricane Maria (e.g.,~\cite{santos2018use, santos2018differential}), Hurricane
Sandy (e.g.,~\cite{kim2016, mongin2017, swerdel2014}), and the 2004 hurricane
season in Florida~\parencite{mckinney2011}.  However, to expand this approach
to study longer time periods for large sets of communities, researchers must be
able to assess exposure to tropical cyclones consistently and comparably across
storms, years, and communities.

@@

However, when epidemiological studies assess exposure to a tropical cyclone
using, as a proxy measurement, how close the storm came to a community, they
may misclassify exposure~\parencite{grabich2015measuring}. While a number of
tropical cyclone hazards are strongly associated with distance from the
tropical cyclone's center (e.g., wind and, at the coast, storm surge and
waves~\parencite{rappaport2000, kruk2010}), other hazards like heavy rainfall,
floods, and tornadoes can occur well away from the tropical cyclone's central
track~\parencite{rappaport2000, atallah2007, moore2012}.  For example, fatal
tropical cyclone tornadoes, which were linked to over~300 deaths in the \ac{US}
between~1995 and~2009, most often occur~200\,--\,500~\si{\kilo\metre} from the
tropical cyclone's center~\parencite{moore2012}.  Further, when studies use
distance from the storm's track to assess exposure, they often use the same
buffer constraints on each side of the storm track
(e.g.,~\cite{kinney2008, currie2013}).  However, the forces of a tropical
cyclone tend to be distributed around its center non-symmetrically.  Extreme
winds are more common to the track's right, where counter-clockwise cyclonic
winds move in concert with the tropical cyclone's forward
motion~\parencite{halverson2015}, and almost all of the fatal tornadoes
associated with \ac{US} tropical cyclones between~1995 and~2009 occurred to the
right of the tropical cyclone's track~\parencite{moore2012}. Rain, conversely,
is often heaviest to the left of the track, especially when the tropical
cyclone interacts with other weather systems~\parencite{atallah2003,
atallah2007, zhu2013variations} or undergoes an extratropical
transition~\parencite{elsberry2002}.  The multi-hazard nature of tropical
cyclones therefore makes it hard to assess exposure based on how close the
storm's central track came to the community.  While other approaches have been
developed to incorporate storm hazards, particulary wind, into exposure
assessment (e.g., \cite{grabich2015measuring, zandbergen2009, czajkowski2011}),
there is not yet a standard approach, and when different studies use different
datasets or storm hazards when assessing storm exposure, it becomes difficult
to compare and aggregate findings from different studies.

>>>>

Hurricanes and other tropical cyclones can severely impact human health in
\ac{US} communities, impacts that have been characterized based on fatality
data from post-disaster surveillance~\parencite{rappaport2000,
rappaport2014fatalities, rappaport2016fatalities, czajkowski2010fatal,
czajkowski2011, moore2012}.  For several types of climate-related
disasters---including heat waves, floods, and wildfires---research based on
post-disaster surveillance data has been richly supplemented by studies
analyzing trends in community-wide administrative or vital data, including time
series or case-crossover studies (e.g.,~\cite{anderson2010heat, son2012impact,
haikerwal2015impact, liu2017wildfire, milojevic2017mental}).  These studies
typically compare the rate of a health outcome in a community during a disaster
to rates during comparable non-disaster periods.  While such studies cannot
attribute specific cases (e.g., a specific death) to a disaster, they
can help characterize the community-wide change in health risk during disasters
and capture impacts that might be missed or underestimated in post-disaster
surveillance.  In many cases, these studies analyze multi-year, multi-community
data, allowing them to estimate average associations over many disasters and to
explore how a disaster's characteristics, or the characteristics of the
community it hits, modify associated health risks
(e.g.,~\cite{anderson2010heat, son2012impact, liu2017wildfire}).  Some studies
have begun to use this approach to study the health impacts of tropical
cyclones, including several studies of Hurricane Maria
(e.g.,~\cite{santos2018use, santos2018differential}), Hurricane Sandy
(e.g.,~\cite{kim2016, mongin2017, swerdel2014}), and the 2004 hurricane season
in Florida~\parencite{mckinney2011}.  However, to expand this approach to study
longer time periods for large sets of communities, researchers must be able to
assess exposure to tropical cyclones consistently and comparably across storms,
years, and communities.

@@

However, when epidemiological studies assess exposure to a tropical cyclone
using, as a proxy, how close the storm came to a community, they
may misclassify exposure~\parencite{grabich2015measuring}. While a number of
tropical cyclone hazards are strongly associated with distance from the
tropical cyclone's center (e.g., wind and, at the coast, storm surge and
waves~\parencite{rappaport2000, kruk2010}), other hazards like heavy rainfall,
floods, and tornadoes can occur well away from the tropical cyclone's central
track~\parencite{rappaport2000, atallah2007, moore2012}.  For example, fatal
tropical cyclone tornadoes, which were linked to over~300 deaths in the \ac{US}
between~1995 and~2009, most often occur~200\,--\,500~\si{\kilo\metre} from the
tropical cyclone's center~\parencite{moore2012}.  Further, when studies use
distance from the storm's track to assess exposure, they often use the same
buffer constraints on each side of the storm track
(e.g.,~\cite{kinney2008, currie2013}).  However, the forces of a tropical
cyclone tend to be distributed around its center non-symmetrically.  Extreme
winds are more common to the track's right, where counter-clockwise cyclonic
winds move in concert with the tropical cyclone's forward
motion~\parencite{halverson2015}, and almost all of the fatal tornadoes
associated with \ac{US} tropical cyclones between~1995 and~2009 occurred to the
right of the tropical cyclone's track~\parencite{moore2012}. Rain, conversely,
is often heaviest to the left of the track, especially when the tropical
cyclone interacts with other weather systems~\parencite{atallah2003,
atallah2007, zhu2013variations} or undergoes an extratropical
transition~\parencite{elsberry2002}.  The multi-hazard nature of tropical
cyclones therefore makes it hard to assess exposure based on how close the
storm's central track came to the community.  While other approaches have been
developed to incorporate storm hazards, particulary wind, into exposure
assessment (e.g., \cite{grabich2015measuring, zandbergen2009, czajkowski2011}),
there is not yet a standard approach, and when different studies use different
datasets or storm hazards when assessing storm exposure, it becomes difficult
to compare and aggregate findings from different studies.

### 2019-11-12 writing/ehp_results.tex
Work some more on abstract and small wording

For maximum sustained surface wind estimates, we found that the primary wind
exposure metric in the open source data generally agreed well with the wind
radii reported in \ac{HURDAT2}. For most storms, $\ge$95\% of counties were
assigned the same category of wind speed ($<$34~\si{\knot};
34\,--\,49.9~\si{\knot}; 50\,--\,63.9~\si{\knot}; $\ge$64~\si{\knot}) by both
data sources (Figure~\ref{fig:windcomparison}).  Disagreement was limited to a
few storms (e.g., Hurricanes Sandy in 2012 and Ike in 2008). For these two
storms, the modeled wind speed values used in the open-source data somewhat
overestimated the extent of the storm's most severe winds at landfall but then
underestimated the extent of 34\,--\,49.9 \si{\knot} storm winds further inland
(Figure~S2). For epidemiology researchers who would like to conduct sensitivity
analysis between these two sets of wind data, we have included estimates from
the \ac{HURDAT2} wind radii as a secondary measure of wind speeds in the
open-source dataset \parencite{hurricaneexposuredata}.

@@

Next, we measured the agreement between exposure classifications for each pair
of hazards, as well as between with a proxy measurement based on
distance from the storm's track. We found that these exposure classifications
typically did not agree strongly between pairs of metrics---the set of counties
identified as ``exposed'' based on one metric often overlapped little with the set
identified as ``exposed'' by another metric, as storms frequently brought
different hazards to different locations.

>>>>

For maximum sustained surface wind estimates, we found that the primary wind
exposure metric in the open-source data generally agreed well with the wind
radii reported in \ac{HURDAT2}. For most storms, $\ge$95\% of counties were
assigned the same category of wind speed ($<$34~\si{\knot};
34\,--\,49.9~\si{\knot}; 50\,--\,63.9~\si{\knot}; $\ge$64~\si{\knot}) by both
data sources (Figure~\ref{fig:windcomparison}).  Disagreement was limited to a
few storms (e.g., Hurricanes Sandy in 2012 and Ike in 2008). For these two
storms, the modeled wind speed values used in the open-source data somewhat
overestimated the extent of the storm's most severe winds at landfall but then
underestimated the extent of 34\,--\,49.9 \si{\knot} storm winds further inland
(Figure~S2). For epidemiology researchers who would like to conduct sensitivity
analysis between these two sets of wind data, we have included estimates from
the \ac{HURDAT2} wind radii as a secondary measure of wind speeds in the
open-source dataset \parencite{hurricaneexposuredata}.

@@

Next, we measured the agreement between exposure classifications for each pair
of hazards, as well as with a proxy measurement based on
distance from the storm's track. We found that these exposure classifications
typically did not agree strongly between pairs of metrics---the set of counties
identified as ``exposed'' based on one metric often overlapped little with the set
identified as ``exposed'' by another metric, as storms frequently brought
different hazards to different locations.
